Tables/Graphs for Article

### 2018-01-08 article/draft1.Rnw
proofread + revisions

Community-driven online question and answer forums (CQA) contain an expansive amount of crowd-sourced knowledge. Thousands of questions and answers are posted by users everyday. One such example of a CQA is iFixit's \textit{Answers} forum. This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users. A reliable measure of the health of these CQAs is question response time. Fast response times enhance user engagement and satisfaction and increase web traffic. This paper presents a survival analysis of the time until a question receives its first answer. A Cox proportional hazards model was developed to predict the survival probability of a question, the probability that a question receives an answer before a certain time. Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = \Sexpr{round(unname(model$stat[8]), 2)}$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.55, 95\% CI = (2.32, 2.80))), factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.88, 95\% CI = (8.20, 9.34))). Future studies can investigate if factors identified as signifcant in this analysis can be generalized to other CQAs.

@@

Community-driven online question and answer forums (CQA) are becoming widely-used sources of information. These online platforms feature thousands of user-posted questions and answers and can receive millions of visits every month. The CQA analyzed in this paper is iFixit's \textit{Answers} forum. Founded in 2003, iFixit's mission is to equip users with the knowledge and tools to repair their broken devices, as part of an effort to save money and reduce electronic waste. This company provides over 30,000 free online repair guides and sells the specialized tools and parts needed for such repairs.

@@

However, analysis and prediction of response times on CQAs have not been thoroughly investigated. There is need for further analysis of response times in these forums, as the majority of existing research focuses on assessing and predicting question and answer quality. This paper presents a survival analysis on the time until a question receives its first answer on iFixit's \textit{Answers} forum, in order to determine factors significantly related to answer time and to predict the ``survival'' probability of a question.

@@

With the recent increase in the popularity and use of CQAs, these data-rich platforms have been the subject of a multitude of studies. Regarding analysis of response times, \cite{Bhat2014} developed a classification model using both textual and non-textual features to estimate response times for questions posted on \textit{Stack Overflow}. \cite{Mahmud2013} used parametric methods and proposed models to predict response times based on exponential distributions. \cite{Asaduzzaman2013} instead focused exclusively on unanswered questions and developed a taxonomy for classifying such questions on \textit{Stack Overflow}, and created a model to predict how long a question would remain unanswered. All research mentioned restricted analysis to either questions for which response times were observed, or to questions that remained unanswered. The research presented in this paper uses the framework of survival analysis, a method not yet applied to CQAs, to allow for analysis of both answered and unanswered questions in a unified framework.

@@

The data analyzed contained 8,025 questions posted from April 8, 2017 to July 7, 2017 (the date the data was downloaded). Variables in the data included: device name and category, title, text, tags, whether or not the user was a member of iFixit's site for less than one day before the question was posted, date and time when the question was posted, and date and time when the first answer was received. Variables derived can be found in Table \ref{table:categorical} and \ref{table:continuous}. See Appendix for more details on variable derivation.

@@

Questions analyzed were restricted to those posted in English. The time until event variable used in survival analysis was defined as the time since posting until a question received its first answer. For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded. Such questions were considered right-censored, meaning that exact answer times for these questions are greater than the observed download time (questions may receive answers after the download date) \cite{Kleinbaum2011}.

@@

As the probability distribution for response times is unknown, a nonparametric Cox proportional hazards model was developed to predict the survival probability of questions \cite{Moore2010}. To build the model, five-fold cross-validation was used \cite{Rodriguez2010}. Univariate analysis, performed on one training set, was used to identify variables to include in the final predictive Cox model \cite{Hammermeister1979}. Each predictor was entered into univarite Cox models, and strength of association with response times was assessed. Those with partial likelihood ratio test p-values of less than 0.001 were included in the final model. Continuous predictors were entered into univariate Cox models both with and without square root and log transformations to determine the form of the predictor to include into the final model. Univariate analysis was again performed on each continuous predictor to investigate the use of splines. Each predictor, with the transformation found necessary in the previous analysis, was fit to three separate Cox models with restricted cubic splines of three, four, and five knots. AIC statistics were used to determine whether or not to include splines, as well as the optimum number of knots \cite{Harrell2015}. All predictors found to be signficant, along with the transformations and functional forms found to be necessary, were included in the model for cross-validation. No variable selection was used after identifying significant predictors in univariate analysis, as \cite{Harrell2015} determined that reducing the number of predictors in the model decreased predictive accuracy more so than including all predictors.

In each fold of cross-validation, the full model was built on the training set and used to generate predicted hazard ratios on the corresponding test set. To assess prediction performance, predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as the survival time. The resulting Nagelkerke's R-square statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were assessed as indicators of the model's performance \cite{Chen}. Signficant results from this model would indicate high predictive accuracy. The partial likelihood ratio assessed is a ratio of the log partial likelihood function evaluated at the parameter estimates, equivalent to a goodness of fit measure of the model with all predictors, and the log partial likelihood function for the null model with no predictors and only the baseline hazard function, equivalent to a goodness of fit measure for the null model. The p-value for this statistic was calculated from the $chi^2$ distribution \cite{find}. Concordance statistics and Somers' \textit{Dxy} are a measure of the model's discriminative ability. Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter response time also has the higher predicted hazard ratio. Concordance statistics close to 1 indicate high discriminative ability, while statistics close to 0.5 indicate discordance, or random predictions. Somers' \textit{Dxy} is the difference between the model's concordance statistic and discordance, 0.5. A Somers' \textit{Dxy} statistic of 0 indicates random predictions, while a statistic equal to 1 indicates perfect predictions \cite{Harrell2015}. These metrics were computed for each iteration on every training and test set. Averages of metrics across training and test sets were evaluated. The final model was then fit to the full data and the same metrics were computed and compared.

@@

  Of 8,025 questions in the full data set, \Sexpr{nrow(x)} were in English (97\% of the full data). Of those questions, \Sexpr{answered} (\Sexpr{percentans}}\%) received an answer by the download date. The shortest response time was \Sexpr{shortest} hours. The longest was \Sexpr{longest} hours (\Sexpr{longest_d} days). Figure ~\ref{fig:answertimes} shows the distribution of response times for all questions analyzed.

@@

  Figure  ~\ref{fig:kmcurve} shows the Kaplan-Meier estimated survival probability for all questions in the data. The curve indicates that if a question does not receive an answer within the first 100 hours after it has been posted, the likelihood of it receiving an answer in the future is low. The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was \Sexpr{mean} hours, or \Sexpr{round(mean / 24, 2)} days. The median survival time, the time at which 50\% of the questions in the data received an answer, was \Sexpr{median} hours. Table \ref{table:quantiles} provides additional percentiles of survival time.

@@

Each training set contained \Sexpr{nrow(train1)} questions, and each test set contained \Sexpr{nrow(test1)} questions. Results of univariate analysis, performed on one training set, are shown in Table \ref{table:univariate_results}. As several continuous predictors contained zeros as values, the log transformation was applied after adding one. All categorical predictors and all continuous predictors marked with an asterisk (*) were entered into the full model.

@@

Average performance metrics for test and training sets and in Table \ref{table:cv}. Partial likelihood ratio statistics and p-values indicate that the model as a whole is signficantly associated with response time. However, its $R^2$ statistic and discrimination indexes are considerably low. Metrics did not change significantly from training to test sets, indicating that the model was not overfit. Metrics for the final model's performance on the full data, also found in \ref{table:cv}, are consistent with metrics found in cross validation and indicate low predictive accuracy.

@@

Assessing the proportional hazards assumption indicated that several levels of the device categorization variable, specifically Apple Product, Camera, Game Console, and Other, violated the assumption. Interpretations of the coefficients highlighted above:

@@

Regarding the model's weak predictive accuracy, it may be explained by limitations in the data. Many users asking a question incorrectly specified the device name (e.g. ``Turtle Beach Ear Force Xmy grandson chewed through the wire while he was playing it's brand-new is there anyway I can have it fixed0 One''), or did not include a device name at all. Many users also incorrectly used the tagging system by including ambiguous and lengthy tags like ``someone sat on it :('' or ``help me please!!!!!'' (tags are generally a couple key words that allow the answering community to quickly discern the question's topic). It is likely that these inconsistencies contributed to the final model's low predictive power. This, along with the results of the final model, reveal some of the ways that the CQA can be structured to improve analysis and decrease response time. As findings indicate that questions with correctly defined tags and device names may lead to quicker response times, the CQA can provide a stricter framework for asking questions. For example, instead of allowing users to enter any device name or tag, which leaves room for user error, the CQA can restrict the tags or devices that users can include to a drop down list. The CQA can also include more tips to guide users asking questions. Establishing and implementing a more restrictive CQA structure can help users to ask understandable and clear questions and decrease response time, as well as create a set of consistent questions for better analysis.

@@

This study developed a Cox proportional hazards model to predict the probability that a question posted on iFixit's \textit{Answers} forum receives an answer before a certain time. Predictors found to be signficant in the model included: device category, if the question was posted on a weekend or a weekday, whether or not the question's text contained at least one word considered frequently-used among unanswered questions, and whether or not the question's title ends in a questionmark. While overall the model was signficant, its predictive performance was considerably low.

@@

% answered question id = 397414
% unanswered question id = 399971
% Table to display questions
\begin{table}[!htbp]
\centering
\begin{tabular}{| l | l | p{6cm} | l |}
  \hline
 \textbf{Answered} & \textbf{Device} & \textbf{Title} & \textbf{Date Posted} \\
  \hline
  Yes & iPhone 6 & iPhone water damage, touch screen issue &  2017-05-10 21:50:48 GMT \\ \cline{2 - 4}
  & \textbf{New User} & \textbf{Text} & \textbf{Date of First Answer} \\ \cline{2 - 4}
  & Yes & So I dropped my iPhone in water 4 days ago. Have done the whole rice thing and seen huge difference in it. However, only one side of my screen works and it is the one side which I need to unlock the phone. What would be the best way forward? & 2017-05-10 23:12:27 GMT \\ \cline{4 - 4}
  & & & \textbf{Response Time (hr)} \\ \cline{4 - 4}
  & & & 1.361 \\ \cline{4-4} \hline
  \textbf{Answered} & \textbf{Device} & \textbf{Title} & \textbf{Date Posted} \\ \cline{1 - 4}
  No & android tablet & ccccaaaan you help me fix my touch screen & 2017-05-23 07:35:12 GMT \\ \cline{2 - 4}
  & \textbf{New User} & \textbf{Text} & \textbf{Date of First Answer} \\ \cline{2 - 4}
  & No & touch screen not worki & NA \\ \cline{4 - 4}
  & & & \textbf{Response Time (hr)} \\ \cline{4 - 4}
  & & & NA \\ 
   \hline
\end{tabular}
\caption{Answered and unanswered questions}
\label{table:questions}
\end{table}

@@

Original device categories, defined by iFixit, included: Apparel, Appliance, Camera, Car and Truck, Computer Hardware, Electronics, Game Console, Household, Mac, Media Player, PC, Phone, Skills, Tablet, Vehicle. Device titles were parsed and certain categories were combined or separated to create a new device categorization variable to use in the Cox model. Categories created included: Android/Other Phone, Apple Product, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle. Under the original device categorization, 1,954 questions (25.2\% of 7,760) were not categorized correctly and indicated an NA for its category. Missing values were a result of users creating questions for devices not already in the iFixit's database, or from the user incorrectly defining the device name. For questions with missing categories, key words were searched for in device titles to recategorize accordingly. All other questions with ambiguous device titles were categorized as Other.

>>>>

Community-driven online question and answer forums (CQA), platforms that allow users to ask and answer questions, contain an extensive amount of crowd-sourced knowledge. Thousands of questions and answers are posted by users everyday. One such example of a CQA is iFixit's \textit{Answers} forum. This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users. A reliable measure of the health of these CQAs is question response time. Fast response times enhance user engagement and satisfaction and increase web traffic. This paper presents a survival analysis of the time until a question receives its first answer. A Cox proportional hazards model was developed to predict the survival probability of a question, the probability that a question receives an answer before a certain time. Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = \Sexpr{round(unname(model$stat[8]), 2)}$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.55, 95\% CI = (2.32, 2.80))), factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.88, 95\% CI = (8.20, 9.34))). Future studies can investigate if factors identified as signifcant in this analysis can be generalized to other CQAs.

@@

Community-driven online question and answer forums (CQA) are becoming widely-used sources of information. These online platforms feature thousands of user-posted questions and answers and can receive millions of visits every month. The CQA analyzed in this paper is iFixit's \textit{Answers} forum. Founded in 2003, iFixit's mission is to equip users with the knowledge and tools necessary to repair their broken devices, as part of an effort to save money and reduce electronic waste. This company provides over 30,000 free online repair guides and sells the specialized tools and parts needed for such repairs.

@@

However, analysis and prediction of response times on CQAs has not been thoroughly investigated. There is need for further analysis of response times in these forums, as the majority of existing research focuses on assessing and predicting question and answer quality. This paper presents a survival analysis on the time until a question receives its first answer on iFixit's \textit{Answers} forum, in order to determine factors significantly related to answer time and to predict the survival probability of a question.

@@

With the recent increase in the popularity and use of CQAs, these data-rich platforms have been the subject of a multitude of studies. Regarding analysis of response times, \cite{Bhat2014} developed a classification model using both textual and non-textual features to estimate response times for questions posted on \textit{Stack Overflow}. \cite{Mahmud2013} used parametric methods and proposed models to predict response times based on exponential distributions. \cite{Asaduzzaman2013} instead focused exclusively on unanswered questions and developed a taxonomy for classifying such questions on \textit{Stack Overflow}, and created a model to predict how long a question would remain unanswered. However, all research mentioned restricted analysis to either questions for which response times were observed or to questions that remained unanswered. The research presented in this paper uses the framework of survival analysis, a method not yet applied to CQAs, to allow for analysis of both answered and unanswered questions in a unified framework.

@@

The data analyzed contained 8,025 questions posted from April 8, 2017 to July 7, 2017 (the date the data was downloaded). Variables in the data included: device name and category, title, text, tags, whether or not the user was a member of iFixit's site for less than one day before the question was posted, date and time the question was posted, and date and time the first answer was received. Variables derived can be found in Table \ref{table:categorical} and \ref{table:continuous}. See Appendix for more details on variable derivation.

@@

Questions analyzed were restricted to those posted in English. The time until event variable used in survival analysis was defined as the time since posting until a question receives its first answer. For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded. Such questions were considered right-censored, meaning that exact answer times for these questions are greater than the observed download time (questions may receive answers after the download date) \cite{Kleinbaum2011}.

@@

As the probability distribution for response times is unknown, a nonparametric Cox proportional hazards model was developed to predict the survival probability of questions \cite{Moore2010}. To build the model, five-fold cross-validation was used \cite{Rodriguez2010}. Univariate analysis, performed on one training set, was used to identify variables to include in the final predictive Cox model \cite{Hammermeister1979}. Each predictor was entered into univarite Cox models and strength of association with response times was assessed. Those with partial likelihood ratio test p-values of less than 0.001 were included in the final model. Continuous predictors were entered into univariate Cox models both with and without square root and log transformations to determine the form of the predictor to include in the final model. Univariate analysis was again performed on each continuous predictor to investigate the use of splines. Each predictor, with the transformation found necessary in the previous analysis, was fit to three separate Cox models with restricted cubic splines of three, four, and five knots. AIC statistics were used to determine whether or not to include splines, as well as the optimum number of knots \cite{Harrell2015}. All predictors found to be signficant, along with transformations and splines found to be necessary, were included in the model for cross-validation. No variable selection was used after identifying significant predictors in univariate analysis, as \cite{Harrell2015} determined that reducing the number of predictors in the model decreased predictive accuracy more so than including all predictors.

In each fold of cross-validation, the full model was built on the training set and used to generate predicted hazard ratios on the corresponding test set. To assess prediction performance, predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as the survival time. The resulting Nagelkerke's R-square statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were assessed as indicators of the model's performance \cite{Chen}. Signficant results from this model would indicate high predictive accuracy. The partial likelihood ratio assessed is a ratio of the log partial likelihood function evaluated at the parameter estimates, equivalent to a goodness of fit measure of the model with predictors, and the log partial likelihood function for the null model without predictors and only the baseline hazard function, equivalent to a goodness of fit measure for the null model. The p-value for this statistic was calculated from the $chi^2$ distribution \cite{find}. Concordance statistics and Somers' \textit{Dxy} are a measure of the model's discriminative ability. Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter response time also has the higher predicted hazard ratio. Concordance statistics close to 1 indicate high discriminative ability, while statistics close to 0.5 indicate discordance, or random predictions. Somers' \textit{Dxy} is the difference between the model's concordance statistic and discordance, 0.5. A Somers' \textit{Dxy} statistic of 0 indicates random predictions, while a statistic equal to 1 indicates perfect predictions \cite{Harrell2015}. These metrics were computed for each iteration on every training and test set. Averages of metrics across training and test sets were evaluated. The final model was then fit to the full data and the same metrics were computed and compared.

@@

  Of 8,025 questions in the full data set, \Sexpr{format(nrow(x), big.mark = ",")} were in English (97\% of the full data). Of those questions, \Sexpr{format(answered, big.mark = ",")} (\Sexpr{percentans}}\%) received an answer by the download date. The shortest response time was \Sexpr{shortest} hours. The longest was \Sexpr{format(longest, big.mark = ",")} hours (\Sexpr{longest_d} days). Figure ~\ref{fig:answertimes} shows the distribution of response times for all questions analyzed.

@@

  Figure  ~\ref{fig:kmcurve} shows the Kaplan-Meier estimated survival probability curve for all questions in the data. The curve indicates that if a question does not receive an answer within the first 100 hours after it has been posted, the likelihood of it receiving an answer in the future is low. The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was \Sexpr{mean} hours, or \Sexpr{round(mean / 24, 2)} days. The median survival time, the time at which 50\% of the questions in the data received an answer, was \Sexpr{median} hours. Table \ref{table:quantiles} provides additional percentiles of survival time.

@@

Each training set contained \Sexpr{format(nrow(train1), big.mark = ",")} questions, and each test set contained \Sexpr{format(nrow(test1), big.mark = ",")} questions. Results of univariate analysis performed on one training set are shown in Table \ref{table:univariate_results}. For continuous predictors that contained zeros, one was added to each observation before applying log transformations. All categorical predictors and all continuous predictors marked with an asterisk (*) were entered into the full model.

@@

Average performance metrics for test and training sets and in Table \ref{table:cv}. Partial likelihood ratio statistics and p-values indicate that the model as a whole is signficantly associated with response time. However, its $R^2$ statistic and discrimination indexes are considerably low. Metrics did not change significantly from training to test sets, indicating that the model was not overfit. Metrics for the final model's performance on the full data, also found in Table \ref{table:cv}, are consistent with metrics found in cross-validation and indicate low predictive accuracy.

@@

Assessing the proportional hazards assumption indicated that several levels of the device categorization variable, specifically Apple Product, Camera, Game Console, and Other, violated the assumption.

Interpretations of the coefficients highlighted in Table \ref{table:coefficients}:

@@

Regarding the model's weak predictive accuracy, it may be explained by limitations in the data. Many users asking a question incorrectly specified the device name (e.g. ``Turtle Beach Ear Force Xmy grandson chewed through the wire while he was playing it's brand-new is there anyway I can have it fixed0 One''), or did not include a device name at all. Many users also incorrectly used the tagging system by including ambiguous and lengthy tags like ``someone sat on it :('' or ``help me please!!!!!'' (tags are generally a couple key words that allow the answering community to quickly discern the question's topic). It is likely that these inconsistencies contributed to the final model's low predictive power. This, along with the results of the final model, reveal some of the ways that the CQA can be structured to improve analysis and decrease response time. As findings indicate that questions with correctly defined tags and device names may lead to quicker response times, the CQA can provide a stricter framework for asking questions. Allowing users to enter any device name or tag leaves room for user error. Instead, the CQA can restrict the tags or devices that users can include to a drop-down list. The CQA can also include more tips to guide users asking questions. Establishing and implementing a more restrictive framework for asking questions can help users ask understandable and clear questions and in turn decrease response time, as well as create a set of consistent questions for improved analysis.

@@

This study developed a Cox proportional hazards model to predict the probability that a question posted on iFixit's \textit{Answers} forum receives an answer before a certain time. Predictors found to be signficant included: device category, if the question was posted on a weekend or a weekday, whether or not the question's text contained at least one word considered frequently-used among unanswered questions, and whether or not the question's title ends in a questionmark. While overall the model was signficant, its predictive performance was considerably low.

@@

% answered question id = 397414
% unanswered question id = 399971
% Table to display questions
\begin{table}[!htbp]
\centering
\begin{tabular}{| l | l | p{6cm} | l |}
  \hline
 \textbf{Answered} & \textbf{Device} & \textbf{Title} & \textbf{Date Posted} \\
  \hline
  Yes & iPhone 6 & iPhone water damage, touch screen issue &  2017-05-10 21:50:48 GMT \\ \cline{2 - 4}
  & \textbf{New User} & \textbf{Text} & \textbf{Date of First Answer} \\ \cline{2 - 4}
  & Yes & So I dropped my iPhone in water 4 days ago. Have done the whole rice thing and seen huge difference in it. However, only one side of my screen works and it is the one side which I need to unlock the phone. What would be the best way forward? & 2017-05-10 23:12:27 GMT \\ \cline{4 - 4}
  & & & \textbf{Response Time (hr)} \\ \cline{4 - 4}
  & & & 1.361 \\ \cline{4-4} \hline \hline
  \textbf{Answered} & \textbf{Device} & \textbf{Title} & \textbf{Date Posted} \\ \cline{1 - 4}
  No & android tablet & ccccaaaan you help me fix my touch screen & 2017-05-23 07:35:12 GMT \\ \cline{2 - 4}
  & \textbf{New User} & \textbf{Text} & \textbf{Date of First Answer} \\ \cline{2 - 4}
  & No & touch screen not worki & NA \\ \cline{4 - 4}
  & & & \textbf{Response Time (hr)} \\ \cline{4 - 4}
  & & & NA \\ 
   \hline
\end{tabular}
\caption{Answered and unanswered questions}
\label{table:questions}
\end{table}

@@

Original device categories defined by iFixit included: Apparel, Appliance, Camera, Car and Truck, Computer Hardware, Electronics, Game Console, Household, Mac, Media Player, PC, Phone, Skills, Tablet, Vehicle. Device titles were parsed and certain categories were combined or separated to create a new device categorization variable to use in the Cox model. Final categories created included: Android/Other Phone, Apple Product, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle. Under the original device categorization, 1,954 questions (25.2\% of 7,760) were categorized incorrectly and indicated an NA for its category. Missing values were a result of users creating questions for devices not already in the iFixit's database, or from the user incorrectly defining the device name. For questions with missing categories, key words were searched for in device titles to recategorize accordingly. All other questions with ambiguous device titles were categorized as Other.

### 2018-01-08 article/draft1.tex
proofread + revisions

Community-driven online question and answer forums (CQA) contain an expansive amount of crowd-sourced knowledge. Thousands of questions and answers are posted by users everyday. One such example of a CQA is iFixit's \textit{Answers} forum. This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users. A reliable measure of the health of these CQAs is question response time. Fast response times enhance user engagement and satisfaction and increase web traffic. This paper presents a survival analysis of the time until a question receives its first answer. A Cox proportional hazards model was developed to predict the survival probability of a question, the probability that a question receives an answer before a certain time. Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = 0.15$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.55, 95\% CI = (2.32, 2.80))), factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.88, 95\% CI = (8.20, 9.34))). Future studies can investigate if factors identified as signifcant in this analysis can be generalized to other CQAs.

@@

  Of 8,025 questions in the full data set, 7760 were in English (97\% of the full data). Of those questions, 4951 (63.8}\%) received an answer by the download date. The shortest response time was 0.5 hours. The longest was 2159.02 hours (89.96 days). Figure ~\ref{fig:answertimes} shows the distribution of response times for all questions analyzed.

@@

  Figure  ~\ref{fig:kmcurve} shows the Kaplan-Meier estimated survival probability for all questions in the data. The curve indicates that if a question does not receive an answer within the first 100 hours after it has been posted, the likelihood of it receiving an answer in the future is low. The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was 775.75 hours, or 32.32 days. The median survival time, the time at which 50\% of the questions in the data received an answer, was 9.16 hours. Table \ref{table:quantiles} provides additional percentiles of survival time.

@@

Each training set contained 6208 questions, and each test set contained 1552 questions. Results of univariate analysis, performed on one training set, are shown in Table \ref{table:univariate_results}. As several continuous predictors contained zeros as values, the log transformation was applied after adding one. All categorical predictors and all continuous predictors marked with an asterisk (*) were entered into the full model.

>>>>

Community-driven online question and answer forums (CQA), platforms that allow users to ask and answer questions, contain an extensive amount of crowd-sourced knowledge. Thousands of questions and answers are posted by users everyday. One such example of a CQA is iFixit's \textit{Answers} forum. This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users. A reliable measure of the health of these CQAs is question response time. Fast response times enhance user engagement and satisfaction and increase web traffic. This paper presents a survival analysis of the time until a question receives its first answer. A Cox proportional hazards model was developed to predict the survival probability of a question, the probability that a question receives an answer before a certain time. Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = 0.15$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.55, 95\% CI = (2.32, 2.80))), factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.88, 95\% CI = (8.20, 9.34))). Future studies can investigate if factors identified as signifcant in this analysis can be generalized to other CQAs.

@@

  Of 8,025 questions in the full data set, 7,760 were in English (97\% of the full data). Of those questions, 4,951 (63.8}\%) received an answer by the download date. The shortest response time was 0.5 hours. The longest was 2,159.02 hours (89.96 days). Figure ~\ref{fig:answertimes} shows the distribution of response times for all questions analyzed.

@@

  Figure  ~\ref{fig:kmcurve} shows the Kaplan-Meier estimated survival probability curve for all questions in the data. The curve indicates that if a question does not receive an answer within the first 100 hours after it has been posted, the likelihood of it receiving an answer in the future is low. The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was 775.75 hours, or 32.32 days. The median survival time, the time at which 50\% of the questions in the data received an answer, was 9.16 hours. Table \ref{table:quantiles} provides additional percentiles of survival time.

@@

Each training set contained 6,208 questions, and each test set contained 1,552 questions. Results of univariate analysis performed on one training set are shown in Table \ref{table:univariate_results}. For continuous predictors that contained zeros, one was added to each observation before applying log transformations. All categorical predictors and all continuous predictors marked with an asterisk (*) were entered into the full model.
